Project Review Template

### 2024-04-26 project-review-Kaggwa.qmd_Erick.qmd
Review by Patrick
Including review by Patrick K.

---
title: Project Review for Mollinedo
author: Xueyan Hu
date: 04-24-2024
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Xueyan Hu

@@

Make sure your final document compiles/knits into a readable, well-formatted html document.

@@

# Specific project content evaluation
Evaluate the different parts of the project by filling in the sections below.

@@

There is an detailed background description and it is easy to understand the current condition of household air pollution. And the transition from introduction to the hypothesis/question is natural and they are highly related.

@@

The questions raised are clear enough and they provide me a rough frame that how the dataset would be organized, what variables it might include, and what kind of analysis the author would apply to the dataset.

@@

The source is provided and the calculating equation is also listed. Although I could have a rough understanding for the raw data, it will be a little better if a codebook is created (I am sorry if I miss this file.)

* source and overall structure of data somewhat explained

@@

The data cleaning process is well organized, all of the cleaning steps are well illustrated, and the processed data looks good to me.

@@

The analysis methods are appropriate for the data in this project according to the type of outcome. And there is a specific model related to environmental analysis involved in this project, different from what models we usually learn during the course. I think it is suitable for data analysis of this project.

@@

Tables are used for presenting the result. A summary is written firstly and then it is divided into several parts for further description. Figure 1 is impressive to me because tt allows me to intuitively find the relationship between variables, especially in the condition that many variables are included it seems really important. The metircs are proper and supplement file is well used.

@@

The study findings are properly discussed with strengths and limitations mentioned, such as linear model can fit the data well and low diversity in answers for categorical variables could lead to bias. And I think both are reasonable.

@@

_Overall, this is a mature, highly completed and meaningful project. From data collection to data cleaning, to the use and supplement of all interpreted figures in the model, every part shows that the project is well organized, and we can also see how much thinking and time the author spent on the project.But there is only one small thing that I would like to mention. There is a folder called R which is created in the template by Dr. Handel. The author haven't used any file in this folder, so I think it could be deleted._

@@

The project is well structured and files are well labeled in the folders. So it is quite easy for me to find all of the relative materials. All of the files have reasonable name. But there is only one folder named 'R' left which should be deleted. And under the result file, maybe 'large file' folder and 'output' folder could also be deleted.

* mostly clear, but some confusing parts (e.g. useless files, things in the wrong folders)

@@

Yes, I think reading through data analysis qmd file, coupled with the contents of the manuscript, I can understand the whole process and don't have much difficulty. But the process of data cleaning is kind of complicated, and it needs to be reviewed back and forth for better understanding, but this is only my own situation.

@@

I have tried all the codes involved in this project and they are fully reproducible. But I haven't found the instruction for reproducing this whole project in the supplement file.
I think it is "fully reproducible without issues" but it will be better if some instructions could be provided.

@@

The overall study is thorough, and both linear and logistic models are used to fit the dataset and the performances are compared, evaluated and discussed in different files. And the result mentioning predictors and the better model that can answer the questions raised above.

@@

* strong level of thoroughness

@@

_I just have a small question. Because only simple linear model and glm are fit in this project, plus the number of variables involved in the data is relatively larger, I wonder if more models could be tried to fit the data to compare the performance and maybe the overfitting problem could also be considered in the discussion part._

>>>>

---
title: Project Review Template 
author: Patrick Kaggwa
date: 04-24-2024
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Patrick Kaggwa

@@

Make sure your final document compiles/renders into a readable, well-formatted html document.

@@

# Specific project content evaluation.

@@

* Context of the Project: 
The project provides a solid background on household air pollution (HAP) in low- and middle-income countries (LMICs). While the background offers a decent summary of previous work, it could be strengthened with more explicit referencing. The project is reasonably well-placed within the existing scientific and public health discourse.
The introduction effectively outlines why the project was undertaken by highlighting the significance of HAP, the limited research on SA in LMICs.

* Areas of improvement 
*Conciseness: 
Some parts of the introduction and background sections contain detailed explanations that could be condensed for brevity without sacrificing clarity. 
* Citations:
While citations are provided throughout the text, there are instances where additional citations could strengthen the claims made. 
* Integration of Pilot Study Findings: 
The introduction briefly mentions the pilot study conducted in Guatemala and Rwanda as part of the HAPIN trial, but it could be more explicit in integrating the findings of this pilot study into the rationale for the current research.

@@

### Feedback and Comments
The questions and hypotheses that the project aims to address are fairly clear and well-described.

@@

### Feedback and Comments
Data Source is well described and the text provides a detailed description of how the data was collected and processed.

#Codebook provided: 
The code book is loaded well

### Summary assessment
* source and overall structure of data well explained

@@

The exploratory data analysis appears sound and is thoroughly documented. The goals for each step were evident, and the coding and procedures were straightforward and easily understandable.

@@

### Feedback and Comments
The analysis appears to be done properly, with appropriate methods used for each component of the analysis. The code is well-explained and provides clear justification for the chosen approaches.
### Summary assessment

@@

Overall, the presentation of the results is well-executed, striking a good balance between textual explanation and visual representation, which enhances the clarity and accessibility of the findings.

@@

Overall, the discussion effectively addresses the study findings, acknowledges both strengths and limitations, and provides a proper interpretation of the results, contributing to a comprehensive understanding of the research outcomes.

@@

Overall, the project demonstrates a strong understanding of the subject matter and presents the findings in a coherent and thoughtful manner.

@@

### Feedback and Comments
The project is well structured but it still has default files and folders which should removed.

### Summary assessment
* well structured

@@

Overall, while the project is reasonably well-documented and understandable.

@@

Everything run smoothly and it reproducible.

@@

Overall the study is thorough.

@@

* strong level of thorougness

@@

_I feel justice was done but remove all unused folders and files as they still exist_
